## Proportional Recruitment

### Models

To simulate and fit proportional recruitment model data, we need to define quantile functions 
parameterized in terms of the mean and variance of the odds of recruits.

For inverse Beta, log Normal and Gamma distributions, define a quantile function and a function 
to generate random deviates. The corresponding random recruits must be scaled by the mean.

```{r}
qInverseBeta <- function(us,mn,vr) { 
  q <- qbeta(us,mn*(mn*(1+mn)+vr)/vr,mn*(1+mn)/vr+2)
  q/(1-q)
}
rInverseBeta <- function(n,mn,vr) { 
  q <- rbeta(n,mn*(mn*(1+mn)+vr)/vr,mn*(1+mn)/vr+2)
  q/(1-q)
}
recInverseBeta<- function(n,mn,vr) { 
  q <- rbeta(n,mn*(mn*(1+mn)+vr)/vr,mn*(1+mn)/vr+2)
  q/(1-q)/mn
}
```

```{r}
qLogNormal <- function(us,mn,vr) {
  qlnorm(us,log(mn^2/sqrt(mn^2 + vr)),sqrt(log(1 + vr/mn^2)))
}
rLogNormal <- function(n,mn,vr) {
  rlnorm(n,log(mn^2/sqrt(mn^2 + vr)),sqrt(log(1 + vr/mn^2)))
}
recLogNormal <- function(n,mn,vr) {
  rlnorm(n,log(mn^2/sqrt(mn^2 + vr)),sqrt(log(1 + vr/mn^2)))/mn
}
```

```{r}
qGamma <- function(us,mn,vr) suppressWarnings(qgamma(us,mn^2/vr,mn/vr))
rGamma <- function(n,mn,vr) rgamma(n,mn^2/vr,mn/vr)
recGamma <- function(n,mn,vr) rgamma(n,mn^2/vr,mn/vr)/mn
```

### Simulation

Generate `n` random age structures and estimate mean and variance of the proportion of recruits
in these samples.
```{r}
prSim <- function(qdist,Msf,n,M,CV,r=1,plus=0,rstdunif=runif) {

  ## Generate deviates
  us <- rstdunif(n*(1-r+length(Msf)+plus))

  ## Compute survivals
  S <- exp(-M*Msf)
  S <- cumprod(c(S[-length(S)],rep(S[length(S)],plus)))
  s0 <- sum(S)

  S <- c(1,S)
  if(r>1) S <- S[r:length(S)]
    
  ## Mean and variance of Q
  mnQ <- 1/s0
  vrQ <- (CV*mnQ)^2

  ## Simulate
  A <- matrix(s0*qdist(us,mnQ,vrQ),length(S))
  N <- S*A
  R <- N[1,]/colSums(N)
  c(mnR=mean(R,na.rm=TRUE), vrR=sd(R,na.rm=TRUE)^2)
}
```


### Stochastic Fits

A model is fitted by generating a sequence of random deviates and adjusting their distribution by 
[probability integral transform](https://en.wikipedia.org/wiki/Probability_integral_transform) to 
match the observed mean and variance of the proportion of recruits.  Not every sequence of deviates
can be transformed to match the observed mean and variance; if the match is not within `tol` of the 
observed values, the function returns `NULL`.   


```{r}
prFit1 <- function(qdist,Msf,mnR,vrR,n,M0,CV0,r=1,plus=0,rstdunif=runif,tol=1.0E-6,max.M=10,max.CV=10) {

  ## Generate deviates
  us <- runif(n*(1-r+length(Msf)+plus))
  
  err <- function(par) {
    ## Compute survivals
    S <- exp(-par[1]*Msf)
    S <- cumprod(c(S[-length(S)],rep(S[length(S)],plus)))
    s0 <- sum(S)

    S <- c(1,S)
    if(r>1) S <- S[r:length(S)]
    
    ## Mean and variance of Q
    mnQ <- 1/s0
    vrQ <- (par[2]*mnQ)^2

    ## Simulate
    A <- matrix(s0*qdist(us,mnQ,vrQ),length(S))
    N <- S*A
    R <- N[1,]/colSums(N)
    (mnR-mean(R,na.rm=TRUE))^2+(sqrt(vrR)-sd(R,na.rm=TRUE))^2
  }
  
  ## Fit the model
  fit <- tryCatch(optim(c(M=M0,CV=CV0),fn=err,method="L-BFGS-B",lower=c(0,0),upper=c(max.M,max.CV)),
                  error=function(.) NULL, warning=function(.) NULL)
  
  ## Recompute parameters
  if(!is.null(fit) && fit$value < tol && fit$par[1] < max.M && fit$par[2] < max.CV) {
    par <- unname(fit$par)
    ## Compute survivals
    S <- exp(-par[1]*Msf)
    S <- cumprod(c(S[-length(S)],rep(S[length(S)],plus)))
    s0 <- sum(S)

    S <- c(1,S)
    if(r>1) S <- S[r:length(S)]
    
    ## Mean and variance of Q
    mnQ <- 1/s0
    vrQ <- (par[2]*mnQ)^2

    c(M=par[1],CV=par[2],mnQ=mnQ,vrQ=vrQ)  
  }
}
```


This version repeatedly tries to fit to model, restarting with a new sequence of random deviates
if a fit fails.  If `max.iter` is not set, this function may never return.
```{r}
prFit <- function(qdist,Msf,mnR,vrR,n,M0,CV0,r=1,plus=0,rstdunif=runif,tol=1.0E-6,max.M=10,max.CV=10,max.iter=Inf) {
  k <- 1
  repeat {
    k <- k+1
    fit <- prFit1(qdist,Msf,mnR,vrR,n,M0,CV0,r,plus,rstdunif,tol,max.M,max.CV)
    if(!is.null(fit) | k>max.iter) return(fit)
  }
}
```



```{r, echo=FALSE, results='hide', purl=FALSE}
knitr::purl("./Source/prfit.Rmd", documentation = 2)
```

