---
title: "Krill Assessment Base Case Subarea 48.1"
author: "Dale Maschette"
date: "03/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

Here we present a base case scenario for the Euphausia superba assessment within Subarea 48.1..... 



```{r}
library(Grym)
library(ggplot2)
library(dplyr)
library(tidyr)
library(furrr)
set.seed(31)
```


# Initial parameters
The initial parameters in this model are largely similar to those of assessments conducted in 2010 with some parameters updated with newer information. The model parameters fall into two broad catagories; 1) those that are derived from data, and 2) those which are decisions as a result of discussions or likely scenarios, for example fishing season or number of time steps.

We are wortking off a 365 day year and assume 8 age classes (0 - 7). 

```{r}
nsteps <- 365 #time steps
Ages <- 0:7 #Age classes
```

Intervals are based off the time steps from a reference date. Intervals can be checked with the `check_dates()` function in the Grym package. Here the assumed reference date is the 1st of October in each year, largely to allow for full summer growth. The year is largely irrelevant so long as 1) you are not using a leap year, and 2) you remember to progress a year if you are going to a month that falls before your reference date. 
```{r}
#reference date
Reference<-"2021/10/01"
#Spawning intervals
check_dates(Reference, "2021/12/15")
check_dates(Reference, "2022/02/15")
#Monitoring intervals
check_dates(Reference, "2022/01/01")
check_dates(Reference, "2022/01/15")
#Fishing intervals
check_dates(Reference, "2022/09/30")


#Interval sequences
spawnI	 <- 76:138
monitorI <- 93:107
fishingI <- 1:365
```

This model uses proportional recruitment estimated with a beta distribution to generate random recruit numbers. For more details see `?prRecruitsGYM`. Inputs are estimated typically from surveys where mean and variance are the proportion of krill in each haul up to a reference age class. In this case the reference age class is 2 year olds, which makes them age class 3 in the model. 

```{r}
#Recruitment Variables
R.mean <- 0.557
R.var <- 0.1^2
R.class <- 3
R.nsurveys <- 17
```

Growth is estimated using a von bertalanffy model and takes the typical inputs for estimating the curve (t0, Linf and K). Growth period is estimated using f0 and f1, unlike the intervals above which are between 1 and 365, the growth period is proportion of the year and is thus between 0 and 1. So a growth period beginning on the 12th increment would have an f0 value of `12/365` or `0.03287671`. 

```{r}
#Growth details 
t0=0.0
K=0.45
Linf=60.8

#Growth Period
check_dates(Reference, "2021/10/21")
check_dates(Reference, "2022/02/12")

f0=21/365
f1=135/365
```

Length and weight relationship values come from the formula W=aL<sup>b</sup> where a gives the slope of the line and b provides the curvature. 
```{r}
#Length Weight
a=1; b=3
```

To provide variance in initial biomass estimates we provide a CV for the log Biomass estimate. 
```{r}
B0logsd <- 0.2
```

In each run, selectivity o-gives are fitted by selecting a value between the minimum and maximum estimates of 50% selectivity and then using the range to provide the lengths at which the curves will rise from 0, and reach 1, passing through the selected 50%. 
```{r}
#Selectivity curve
sel50Min<-30
sel50Max<-35
selrange<-11
```

In the same manner as selectivity, for each run maturity o-gives are fitted by selecting a value between the minimum and maximum estimates of 50% selectivity and then using the range to provide the lengths at which the curves will rise from 0, and reach 1, passing through the selected 50%. 
```{r}
#Maturity Curve
mat50Min<-31
mat50Max<-36
matrange<-12
```

# Running the model.
Now that the model parameters have been set, we load the `KrillProjection` function. 

```{r}
source('Projection_function.R')
```

We then put all our input parameters into the `KrillProjection` function (in this order) and create the `Project` function. Each time we run `Project()` is an individual run of the Grym and how we do our assessment. 

```{r}
Project<-KrillProjection(nsteps, Ages,					 #time step numbers and age classes
								 spawnI,monitorI,fishingI,			 #Interval sequences
								 R.mean,R.var,R.class,R.nsurveys,#Recruitment Variables
								 t0,K,Linf,f0,f1,								 #Growth details 
								 a, b, 								 					 #Length/Weight Details
								 sel50Min,	sel50Max,	selrange,	 #Selectivity Parameters
								 mat50Min,	mat50Max,	matrange,  #Maturity parameters
								 B0logsd,
								 gamma=c(0,0.04,0.08,0.1,0.139,0.15,0.2),n.years=20 #Test details
								 )
```

Running the assessment becomes a simple matter of doing `Project()` over and over again. To do this quickly we use `future_map_dfr()` from the furrr package. This lets use use parallel processing to significantly speed up the assessments. 
`plan()` sets up the type of processing to be used (multiprocess) and the number or cores to be used (workers), which here we have set to the number of cores available-2. It is wise not to have the number of cores used >= the number of cores available. 

Setting `plan()` back to sequential tells R to stop parallel processing. 

```{r}
Runs<-201

plan(multiprocess, workers= availableCores()-2)
df_48_1 <- future_map_dfr(1:Runs,Project,.options = furrr_options(seed = TRUE))
plan(sequential)
```

Save the Grym output for record. 

```{r}
saveRDS(df_48_1, file="48.1_Grym_output.rds")
```


# Evaluating the results
The decision rules for krill are: 
	
	1. Choose a yield, gamma1, so that the probability of the spawning biomass dropping below 20% of its median pre-exploitation level over a 20-year harvesting period is 10%.

	2. Choose a yield, gamma2, so that the median escapement at the end of a 20 year period is 75% of the median pre-exploitation level.

	3. Select the lower of gamma1 and gamma2 as the yield.

gamma1:
```{r, warning=FALSE}
Gamma1 <- df_48_1 %>% group_by(Gamma,Run) %>% 
	summarize(Dep=min(SSB/SSB0)) %>% 
	summarize(Pr=mean(Dep < 0.2))
Gamma1
#Given the gamma values tested, gamma 1 is:
Gamma_1 <- max(Gamma1$Gamma[Gamma1$Pr<=0.1])
Gamma_1

#What is the approximate Gamma that meets 10% depletion to test.
approx(Gamma1$Pr,Gamma1$Gamma,0.1)$y
```

gamma2: 
```{r}
#Gamma 2:
Gamma2 <- df_48_1 %>%  group_by(Gamma) %>% 
	filter(Year %in% max(Year)) %>% 
	summarise(ssb=median(SSB),ssb0=median(SSB0))

Gamma2$Escapement<-Gamma2$ssb/Gamma2$ssb0

Gamma2

#Given the gamma values tested, gamma 2 is:
Gamma_2<-max(Gamma2$Gamma[Gamma2$Escapement>=0.75])

#What is the approximate Gamma that meets 75% escapement to test.
approx(Gamma2$Escapement,Gamma2$Gamma,0.75)$y

```

Select the gamma which is lowest. 
```{r}
#The actual Gamma is the smallest of the two gammas:
GammaToUse<-which(c(Gamma_1,Gamma_2)==min(Gamma_1,Gamma_2)) #Which gamma is min?
if(length(GammaToUse)==2){GammaToUse=3} #when gamma1 and gamma2 are equal
OUT<-cbind(Gamma_1,Gamma_2,GammaToUse)
OUT
```

